Low Complexity Adaptive Sonar Imaging

### 2016-02-22 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2016:02:22	15:58:01	(ma.22.feb.)

In this study we expand our previous work of applying LCA to active sonar imaging~\cite{Buskenes2011}. We use variations of the parametric Kaiser window, but also compare it to the trigonometric window function. We extend Synnev\aa{}g's work by steering all our windows and not just some, and demonstrate how LCA's performance is affected by the type and number of windows included. Our results are obtained using experimental data from the 32 element Kongsberg Maritime HISAS 1030 synthetic aperture sonar (SAS), which operates at 100\,kHz with an element beamwidth of 23$^\circ$.

@@

To test the performance of the MVDR and LCA beamformers, we have processed data acquired by the Kongsberg Maritime HUGIN AUV carrying their 32 element HISAS1030 sonar~\cite{Hansen2011}. It is a high resolution synthetic aperture sonar with 1.2\;m array length, 100\;kHz operating frequency, 30\;kHz bandwidth and 23$^\circ$ receiver element beamwidth.

>>>>

In this study we expand our previous work of applying LCA to active sonar imaging~\cite{Buskenes2011}. We use variations of the parametric Kaiser window, but also compare it to the trigonometric window function. We extend Synnev\aa{}g's work by steering all our windows and not just some, and demonstrate how LCA's performance is affected by the type and number of windows included. Our results are obtained using experimental data from the 32 element Kongsberg Maritime HISAS 1030 synthetic aperture sonar (SAS), which operates at 100\,kHz with an -3\,dB element opening angle of 23$^\circ$.

@@

To test the performance of the MVDR and LCA beamformers, we have processed data acquired by the Kongsberg Maritime HUGIN AUV carrying their 32 element HISAS1030 sonar~\cite{Hansen2011}. It is a high resolution synthetic aperture sonar with 1.2\;m array length, 100\;kHz operating frequency, 30\;kHz bandwidth and 23$^\circ$ receiver element -3\,dB opening angle.

### 2016-02-22 LCAforActiveSonarImaging/submission/submit1/answer/answer.tex
la2pdf commit - 2016:02:22	15:58:01	(ma.22.feb.)

\begin{enumerate}
% \emph{General}
\hi{Introduction}
\qi{The authors show no evidence that bats use adaptive processing, remove this example.}
\ai{The reviewer makes a good point, this may not have been obvious. We have provided a reference for the adaptive processing used by bats, but would prefer to keep the example if possible.}
%
\qi{It is not clear whether LCA is really an adaptive method that adapts weights on the fly or a method that a posteriori decides which window shows best results.}
\ai{We appreciate the remark. We are using a system level definition of adaptivity that includes any kind of dynamic and data dependent behaviour, hence feel that both beamformers fall in that category. Both methods process the pixels in a data dependent manner, however, perhaps it should be made even clearer that the LCA solution space is a sampled version of that of MVDR. We will attempt to express this better.}
%
\qi{The use of non-SI units like cm is discouraged.}
\ai{We agree that non-SI units should be avoided, however had the belief that cm being a prefixed SI unit was valid? In the IEEE Styles Manual this unit is used several times as an example: 
\url{http://www.ieee.org/publications_standards/publications/journmag/online_style_manual-10292015.pdf} (e.g. on page 24 paragraph ``The En, Em, or Two-Em Dash'', and several times on page 25 paragraph ``Math'' bullet point 16). Will leave this as is for now pending an answer for this.}
%
\end{enumerate}

@@

\begin{enumerate}
% \emph{General}
\hi{Abstract}
\qi{"the array's spatial covariance matrix" might be a bit shocking for the non-expert Reader --> The formulation in the Introduction might fit better "the incluence of noise ..."}
\ai{This is a good point. We have reformulated the sentence to speak of computing the spatial statistics instead.}
%
\hi{Page 2}
\qi{"6 of which were micro-steered" --> a short explanation or reference might help to understand what is meant by "micro-steered"}
\ai{Nice catch. A short sentence elaborating on this expression added.}
%
\qi{"it was not clear how how many" --> delete 1 x "how"}
\ai{Thank you. Corrected.}
%
\qi{"with an element beamwidth" --> what is meant by element beamwidth? Maybe an additional figure could be used to explain this.}
\ai{}
%
\hi{Page 3, after (1)}
\qi{"Applying a window that trails off .... Minimum variance distortion-less response (MVDR) beamformer."--> real and complex Windows? The introduction should be more formal: x ist introduced as delayed data, weights or delays to change, or both is explained later. --> The difference between noise and sidelobes should be pointed out.}
\ai{}
%
\hi{Page 5, equation (5)}
\qi{The lateral correlation and the reason why equation (5) is a good choice should be better explained.}
\ai{}
%
\hi{Page 6, last row}
\qi{"they are optimal for any value" --> optimal in which sense?}
\ai{Thank you. This was mentioned earlier in the same paragraph, just after (8).}
%
\hi{Fig 3}
\qi{why is a 40x40 pixel group a good choice? could the associated broadside direction be made visible in the figure, too?}
\ai{This is an excellent question. This should perhaps be related to the detail level in the image, which in turn depends on the array's imaging performance.}
%
\hi{Page 8}
\qi{reference to Fig.1 --> could the sequence of figures be changes to have Fig. 1 closer to this paragraph}
\ai{Valid point. In our two column print the figure is on the page before its first reference. }
%
\hi{Page 11}
\qi{where is the synthetic aperture needed/applied in this work, or is it just the name of the array? how does the work on LCA/MVDR Change the Quality of synthetic aperture?
what exactly is the sectorscan mode?}
\ai{Thank you, we see that our formulation should be clarified. We are creating an image of the sector highlighted by a single ping of data (sectorscan), but are using data recorded by a synthetic aperture sonar (SAS). We mention it since SAS systems have a wide transmit beam intended to highlight multiple pings and thus does not produce the best sectorscan images.}
%
\end{enumerate}

>>>>

\begin{enumerate}
% \emph{General}
\hi{Introduction}
\qi{The authors show no evidence that bats use adaptive processing, remove this example.}
\ai{The reviewer makes a good point, this may not have been obvious. We have provided a reference for the adaptive processing used by bats, but would prefer to keep the example if possible.}
%
\qi{It is not clear whether LCA is really an adaptive method that adapts weights on the fly or a method that a posteriori decides which window shows best results.}
\ai{We appreciate the remark. We are using a system level definition of adaptivity that includes any kind of dynamic and data dependent behaviour, hence feel that both beamformers fall in that category. Both methods process the pixels in a data dependent manner, and result in non linear image. However, perhaps it should be made even clearer that the LCA solution space is a sampled version of that of MVDR. We will attempt to express this better.}
%
\qi{The use of non-SI units like cm is discouraged.}
\ai{We agree that non-SI units should be avoided, however had the belief that cm being a prefixed SI unit was valid? In the IEEE Styles Manual this unit is used several times as an example: 
\url{http://www.ieee.org/publications_standards/publications/journmag/online_style_manual-10292015.pdf} (e.g. on page 24 paragraph ``The En, Em, or Two-Em Dash'', and several times on page 25 paragraph ``Math'' bullet point 16). Will leave this as is for now pending an answer for this.}
%
\end{enumerate}

@@

\begin{enumerate}
% \emph{General}
\hi{Abstract}
\qi{"the array's spatial covariance matrix" might be a bit shocking for the non-expert Reader --> The formulation in the Introduction might fit better "the incluence of noise ..."}
\ai{This is a good point. We have reformulated the sentence to speak of computing the spatial statistics instead.}
%
\hi{Page 2}
\qi{"6 of which were micro-steered" --> a short explanation or reference might help to understand what is meant by "micro-steered"}
\ai{Nice catch. A short sentence elaborating on this expression is added.}
%
\qi{"it was not clear how how many" --> delete 1 x "how"}
\ai{Thank you. Corrected.}
%
\qi{"with an element beamwidth" --> what is meant by element beamwidth? Maybe an additional figure could be used to explain this.}
\ai{Good remark. We meant the -3dB opening angle of the elements on transmit. This has now been reworded.}
%
\hi{Page 3, after (1)}
\qi{"Applying a window that trails off .... Minimum variance distortion-less response (MVDR) beamformer."--> real and complex Windows? The introduction should be more formal: x ist introduced as delayed data, weights or delays to change, or both is explained later. --> The difference between noise and sidelobes should be pointed out.}
\ai{}
%
\hi{Page 5, equation (5)}
\qi{The lateral correlation and the reason why equation (5) is a good choice should be better explained.}
\ai{Indeed it should, this paragraph is now rewritten.}
%
\hi{Page 6, last row}
\qi{"they are optimal for any value" --> optimal in which sense?}
\ai{Thank you. This was mentioned earlier in the same paragraph, just after (8).}
%
\hi{Fig 3}
\qi{why is a 40x40 pixel group a good choice? could the associated broadside direction be made visible in the figure, too?}
\ai{This is an excellent question. This should perhaps be related to the detail level in the image, which in turn depends on the array's imaging performance.}
%
\hi{Page 8}
\qi{reference to Fig.1 --> could the sequence of figures be changes to have Fig. 1 closer to this paragraph}
\ai{Valid point. In our two column print the figure is on the page before its first reference. }
%
\hi{Page 11}
\qi{where is the synthetic aperture needed/applied in this work, or is it just the name of the array? how does the work on LCA/MVDR Change the Quality of synthetic aperture?
what exactly is the sectorscan mode?}
\ai{Thank you, we see that our formulation should be clarified. We are creating an image of the sector highlighted by a single ping of data (sectorscan), but are using data recorded by a synthetic aperture sonar (SAS). We mention it since SAS systems have a wide transmit beam intended to highlight multiple pings and thus does not produce the best sectorscan images.}
%
\end{enumerate}
